Supplimentary Analysis

### 2021-11-12 Supplymentary.Rmd
* renv is removed. pacman is used install packages

```{r factordetailsAppB, include=FALSE}
#Preparing the EFA table
library(data.table)
fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(2)
  #supress loadings
  loadings[abs(loadings) < abs(cut)] <- ""
  #get additional info
  add_info <- cbind(x$communality, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
    rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")
  #build table
  loadings <- loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(across(where(is.numeric), round, 3)) %>% 
    as.data.frame()
  variance <- x$Vaccounted %>% 
  as.data.frame()%>% 
  round(2)
  loadings <- rbind(setDT(loadings), setDT(variance[2,]), fill=TRUE)

}

efa.table <- fa_table(fa.5F.4,.3) 
nr <- nrow(efa.table)
efa.table[nr, 1] <- "% of Variance"

>>>>

```{r factordetailsAppB, include=FALSE}
#Preparing the EFA table

efa.table <- tabledown::fac.tab(fa.5F.4,.3)

### 2021-11-12 Supplymentary.tex
* Successfully Knitting with appendix but formating is not right
* Table 2 is now formatted * Polygon edge not found error is solved.
* installation script is uploaded
* renv is removed. pacman is used install packages

\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}

@@

\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}

@@

\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}

@@

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}

@@

\caption{Correlation plot of the items}(\#fig:figCorAppB)
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/facIdFigAppB-1}

@@

\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB)
\end{figure}

@@

\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}

@@

\begin{tabular}{ccccccccc}
\toprule
item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
\midrule
item19 & 0.99 &  &  &  &  & 1.01 & -0.01 & 1.06\\
item20 & 0.91 &  &  &  &  & 0.87 & 0.13 & 1.11\\
item18 & 0.82 &  &  &  &  & 0.71 & 0.29 & 1.12\\
item21 & 0.8 &  &  &  &  & 0.68 & 0.32 & 1.16\\
item4 & 0.47 &  &  &  &  & 0.25 & 0.75 & 1.30\\
item11 &  & 0.83 &  &  &  & 0.69 & 0.31 & 1.01\\
item10 &  & 0.81 &  &  &  & 0.67 & 0.33 & 1.03\\
item12 &  & 0.56 &  &  &  & 0.37 & 0.63 & 1.37\\
item8 &  & -0.44 &  &  &  & 0.21 & 0.79 & 1.11\\
item7 &  & 0.42 &  &  &  & 0.23 & 0.77 & 1.61\\
item9 &  & 0.33 &  &  &  & 0.12 & 0.88 & 1.10\\
item16 &  &  & 0.95 &  &  & 0.95 & 0.05 & 1.10\\
item17 &  &  & 0.74 &  &  & 0.60 & 0.41 & 1.17\\
item36 & 0.3 &  & 0.73 &  &  & 0.65 & 0.35 & 1.43\\
item3 &  &  &  & 0.85 &  & 0.75 & 0.25 & 1.05\\
item27 &  &  &  & 0.78 &  & 0.62 & 0.38 & 1.03\\
item40 &  &  &  & 0.71 &  & 0.51 & 0.49 & 1.05\\
item35 &  &  &  &  & 0.58 & 0.35 & 0.65 & 1.09\\
item48 &  &  &  &  & 0.57 & 0.35 & 0.65 & 1.14\\
item33 &  &  &  &  & 0.55 & 0.32 & 0.68 & 1.08\\
item47 &  &  &  &  & 0.52 & 0.29 & 0.71 & 1.19\\
item44 &  &  &  &  & 0.45 & 0.22 & 0.78 & 1.15\\
item31 &  &  &  &  & 0.41 & 0.21 & 0.79 & 1.48\\
item38 &  &  &  &  & 0.33 & 0.13 & 0.87 & 1.32\\
\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 & NA & NA & NA\\
\bottomrule
\addlinespace
\end{tabular}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Five Factor Solution{[}Unmerged Responses{]} (24 Items)}
\end{minipage} \\
\midrule
\endhead
\textbf{F1} \\
I use light therapy applying a blue light box. \\
I use light therapy applying a light visor. \\
I use light therapy applying a white light box. \\
I use light therapy applying another form of light device. \\
I use an alarm with a dawn simulation light. \\
\textbf{F2} \\
I spend more than 3 hours per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I spend 30 minutes or less per day (in total) outside. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
\textbf{F3} \\
I look at my mobile phone screen immediately after waking up. \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I check my phone when I wake up at night. \\
\textbf{F4} \\
I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. \\
I seek out knowledge on how to improve my light exposure. \\
I dim my computer screen within 1 hour before attempting to fall
asleep. \\
I discuss the effects of light on my body with other people. \\
I modify my light environment to match my current needs. \\
I dim my room light within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
\textbf{F5} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
hour before attempting to fall asleep. \\
\bottomrule
\end{longtable}
\end{appendix}

>>>>

\caption{\label{tab:MinResTab-31}Factor loadings and communality of the retained items(Minmum Residual)}

@@

\caption{\label{tab:sixFacTab-33}Factor loadings and communality of the retained items(six factor)}

@@

\caption{\label{tab:tabDesAppB-37}Descriptive Statistics for Unmerged response options}

@@

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-39-1}

@@

\caption{Correlation plot of the items}(\#fig:figCorAppB-39)
\end{figure}

@@

{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-43-1}

@@

\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-43)
\end{figure}

@@

\caption{\label{tab:EFATableAppB-46}Factor loadings and communality of the retained items [Unmerged Responses]}

@@

\begin{tabular}{ccccccccc}
\toprule
item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
\midrule
item19 & 0.99 &  &  &  &  & 1.007 & -0.007 & 1.058\\
item20 & 0.91 &  &  &  &  & 0.874 & 0.126 & 1.114\\
item18 & 0.82 &  &  &  &  & 0.711 & 0.289 & 1.123\\
item21 & 0.8 &  &  &  &  & 0.683 & 0.317 & 1.163\\
item4 & 0.47 &  &  &  &  & 0.25 & 0.75 & 1.298\\
item11 &  & 0.83 &  &  &  & 0.687 & 0.313 & 1.007\\
item10 &  & 0.81 &  &  &  & 0.67 & 0.33 & 1.031\\
item12 &  & 0.56 &  &  &  & 0.371 & 0.629 & 1.374\\
item8 &  & -0.44 &  &  &  & 0.206 & 0.794 & 1.106\\
item7 &  & 0.42 &  &  &  & 0.226 & 0.774 & 1.614\\
item9 &  & 0.33 &  &  &  & 0.115 & 0.885 & 1.1\\
item16 &  &  & 0.95 &  &  & 0.946 & 0.054 & 1.097\\
item17 &  &  & 0.74 &  &  & 0.595 & 0.405 & 1.168\\
item36 & 0.3 &  & 0.73 &  &  & 0.653 & 0.347 & 1.431\\
item3 &  &  &  & 0.85 &  & 0.746 & 0.254 & 1.048\\
item27 &  &  &  & 0.78 &  & 0.624 & 0.376 & 1.028\\
item40 &  &  &  & 0.71 &  & 0.512 & 0.488 & 1.05\\
item35 &  &  &  &  & 0.58 & 0.351 & 0.649 & 1.091\\
item48 &  &  &  &  & 0.57 & 0.354 & 0.646 & 1.144\\
item33 &  &  &  &  & 0.55 & 0.32 & 0.68 & 1.085\\
item47 &  &  &  &  & 0.52 & 0.294 & 0.706 & 1.186\\
item44 &  &  &  &  & 0.45 & 0.216 & 0.784 & 1.145\\
item31 &  &  &  &  & 0.41 & 0.206 & 0.794 & 1.477\\
item38 &  &  &  &  & 0.33 & 0.129 & 0.871 & 1.317\\
\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 &  &  & \\
\bottomrule
\addlinespace
\end{tabular}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Five Factor Solution{[}Unmerged Responses{]} (24 Items)}
\end{minipage} \\
\midrule
\endhead
\textbf{F1} \\
I use light therapy applying a blue light box. \\
I use light therapy applying a light visor. \\
I use light therapy applying a white light box. \\
I use light therapy applying another form of light device. \\
I use an alarm with a dawn simulation light. \\
\textbf{F2} \\
I spend more than 3 hours per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I spend 30 minutes or less per day (in total) outside. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
\textbf{F3} \\
I look at my mobile phone screen immediately after waking up. \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I check my phone when I wake up at night. \\
\textbf{F4} \\
I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. \\
I seek out knowledge on how to improve my light exposure. \\
I dim my computer screen within 1 hour before attempting to fall
asleep. \\
I discuss the effects of light on my body with other people. \\
I modify my light environment to match my current needs. \\
I dim my room light within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
\textbf{F5} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
hour before attempting to fall asleep. \\
\bottomrule
\end{longtable}

{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-47-1}

\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-47)
\end{figure}
\end{appendix}

### 2021-11-12 manuscript.Rmd
* renv is removed. pacman is used install packages

```{r depMan, include=FALSE}
#renv::init()
#renv::snapshot()
#renv::status()
renv::restore()
```

@@

#seperating naming and  reducing data for descriptive Table 
desctable.data <- select(descriptives.data, c(listdescVars,
                          IncludedInCFA))

@@

gt.cfa.long <- gather(gt.cfa.data.table, Items, value)
gt.cfa.long$value <- as.numeric(as.character(gt.cfa.long$value))
gt.cfa.tab <- gt.cfa.long %>% 
  group_by(Items) %>% 
# calculate summary stats & create data for the histogram and density plot
  summarise(
    nr = n(),
    mean = mean(value, na.rm = TRUE),
    med = median(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    hist_data = list(value),
    dens_data = list(value),
    .groups = "drop"
  ) %>%

@@

>>>>

```{r pacman, include=FALSE}
#You need to run this chunck 1X in your system 
#install.packages("pacman")
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem)
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja","crsh/citr", "masiraji/tabledown")
pacman::p_install_gh("masiraji/tabledown")

@@

#seperating naming and  reducing data for descriptive Table 
desctable.data <- dplyr::select(descriptives.data, c(listdescVars,
                          IncludedInCFA))

@@

gt.cfa.long <- gather(gt.cfa.data.table, Items, value)
gt.cfa.long$value <- as.numeric(as.character(gt.cfa.long$value))
gt.cfa.tab <- gt.cfa.long %>% 
  group_by(Items) %>% 
# calculate summary stats & create data for the histogram and density plot
  dplyr::summarise(
    nr = n(),
    mean = mean(value, na.rm = TRUE),
    med = median(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    hist_data = list(value),
    dens_data = list(value),
    .groups = "drop"
  ) %>%

@@

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('Supplymentary.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('instrument.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('Supplymentary.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('instrument.Rmd')
```
